---
title: "rzaia.Rmd.Homework4"
author: "Rafael Zaia"
date: '2022-11-05'
output: html_document
---


## Question 1: The data set “soybean_yield.csv” present soybean yield bushels/acre under two conditions, with and without a given fertilizer. Conduct a statistical test to show if the application of that giver fertilizer results in a higher yield.

```{r}
## Importing Data
soybean_yield <- read.csv("~/Documents/Data_homework4/soybean_yield.csv")

## Installing Packages
library(tidyverse)
library(gapminder)


## analysing the boxplot
boxplot(soybean_yield)

## Ho: yield with fertilizer = yield with no fertilizer
## Two-sided test
## assume non-equal variances


t.test(soybean_yield, mu=0, alt = "two.sided", conf=0.95, var.equal=F, vari.equal=F)

## The data provide very strong evidence (P<0.0005) that giver fertilizer results in a higher yield.


```
## Question 2: In an experiment evaluating leaf nitrogen concentration, the researcher measures the greenness of the same leaves before and after applying a nitrogen-based fertilizer. Using the “nitrogen.csv” data set, answer the following question: is this fertilizer effective and increasing leaf nitrogen (making it “greener”)?

```{r}
## Importing data
nitrogen <- read.csv("~/Documents/Data_homework4/nitrogen.csv")

## Ploting data
boxplot(nitrogen)

## Ho: Fertilizer affect leaf nitrogen concentration = no fertilizer no affect leaf nitrogen concentration 
## Two-sided test
## Assume no-equal variance

t.test(nitrogen, mu=0, alt = "two.sided", conf=0.95, var.equal=F, vari.equal=F)

## The data provide very strong evidence (P<0.0005) that giver fertilizer results in a leaf greener. 

```
## Question 3: A researcher wanted to know the percent change in UARK students’ weight after the consumption of a new diet. Thus, they evaluated 9 CSES students before and after new died. The percent changes are c(0.7, 3.5, 4, 4.9, 5.5, 7, 7.4, 8.1, 8.4).

## a) What is the null and alternative hypothesis?
#Ho: weight before = weight after new diet --> mean = 0
#Ha: mean < 0 
## b) Is it appropriate to conduct a t-test in this case?Explain.
#Yes, this is an example of the one-sample t test. We draw a random sample of size n from an N(mean, sd) population. When s is estimated from the sample, the distribution of the test statistic t is a t distribution with df = n -1. 
## 

## Question 4: Seeds are randomly assigned to be planted in pots with soil treated with pesticide or in pots with untreated soil. Seedling growth (in mm) is recorded after 2 weeks.
```{r}
## Importing the data
growth <- read.csv("~/Documents/Data_homework4/growth.csv")

## Ploting the data
ggplot(growth, mapping = aes(x=variable, y=Measure, fill=variable)) + geom_boxplot(show.legend = FALSE) + 
  geom_jitter()

## a) What are the 90% and the 99% confidence interval for the seedling growth?  

# H0: mean is equal 0
# two-sided test

names(growth)
dim(growth)
growth[1:3,]
t.test(growth$variable, growth$Measure, mu=0, alt="two.sided", paired=TRUE, conf.level=0.90)
```

## Question 5: I am interested in evaluating the proportion of individuals who recovered from COVID- 19 in Fayetteville. What number of individuals would I need to sample to obtain a margin of error of 0.02 with a 95% confidence interval?

# For a 95% confidence interval, z* =  1.96

n = (z*0.02)